MSDS 6306: Doing Data Science - Case Study 01 - Beers/Breweries Dataset

### 2020-10-11 MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Update MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd

```{r Brewery Data}
# This reads in the Beers data from select folder file Breweries.csv.
Breweriesdata <- read.csv(choose.files(),header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
head(Breweriesdata)
nrow(Breweriesdata)
```

>>>>

```{r Brewery Data}
# This reads in the Beers data from select folder file Breweries.csv.
Breweriesdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Breweries.csv",header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
head(Breweriesdata)
nrow(Breweriesdata)
```
